\thetitle

### 2021-03-03 writing/related.tex
space war
emphasizing difference with POPL paper

Technically, this work and~\citet{lksfd-popl-2020}'s differ in many ways. The
experiment presented here concerns three different modes of gradual typing,
theirs a single notion of contract checking.  It also contributes the idea of
creating three comparable rational programmers (with several modes). The
type-level mutators represent another technical contribution of the work
presented here; as explained in section~\ref{sec:mutate}, almost none
of~\citet{lksfd-popl-2020}'s mutators is useful at the level of type mistakes.

>>>>

At a technical level, this work and~\citet{lksfd-popl-2020}'s differ in
many ways. The experiment presented here concerns three different modes of
gradual typing, theirs a single notion of contract checking.  It also
contributes the idea of creating three comparable rational programmers
(with several modes). Thus the method of this paper answers whether blame
adds value to a gradual type system and what gradual type system it
benefits the most; while~\citet{lksfd-popl-2020} only establish a
systematic relation between blame for contracts and behavioral bugs .The
type-level mutators represent another technical contribution of the work
presented here; as explained in section~\ref{sec:mutate}, almost none
of~\citet{lksfd-popl-2020}'s mutators is useful at the level of type
mistakes.
